\documentclass{resume} % Use the custom resume.cls style
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{fontspec}
\setmainfont{Calibri}[
  Path=./,
  Extension=.ttf,
  UprightFont=*,
  BoldFont=*-b,
  ItalicFont=*-i,
  BoldItalicFont=*-z,
]
\usepackage{geometry}
\usepackage[normalem]{ulem}
\usepackage{enumitem}
\newgeometry{left=0.8cm, right=0.8cm, top=0.45cm, bottom=0.55cm}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\definecolor{oinkblue}{rgb}{.08,.34,.5}
\hypersetup{
    colorlinks=true,
    allcolors=oinkblue,
}
\makeatletter
\begingroup
  \catcode`\$=6 %
  \catcode`\#=12%
  \gdef\href@split$1#$2#$3\\$4{%
    \hyper@@link{$1}{$2}{\uline{$4}}%
    \endgroup
  }%
\endgroup
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{ESTER CHEN}
\address{
\href{mailto:esterchen@mail.rit.edu}{esterchen@mail.rit.edu} |
+1 (236)-897-9906 |
Rochester, NY |
\href{https://esterchen1231.github.io}{Website} |
\href{https://www.linkedin.com/in/esterchen}{LinkedIn} |
\href{https://scholar.google.com/citations?user=cBErukUAAAAJ}{Scholar}
}

\begin{document}
\footnotesize

\begin{rSection}{Applied Research Profile}
Ph.D. researcher in human-AI systems, accessibility, and visualization with experience designing experiments, analyzing large behavioral datasets, building Python/SQL data workflows, and translating research into product, UX, and e-commerce strategy decisions. Published in ACM CHI/CSCW and AAAI ICWSM.
\end{rSection}

\begin{rSection}{Education}
{\makebox[7cm][l]{\bf Rochester Institute of Technology, US}{\textbf{\textit{\\Ph.D. Student, Computing \& Information Sciences}}}\hfill{Aug. 2024 -- Present}}\\
{\makebox[7cm][l]{\bf Penn State University, US}{\textbf{\textit{\\M.Sc. Informatics, Human-Centered Design}}}\hfill{Aug. 2022 -- May 2024}}\\
{\makebox[7cm][l]{\bf BrainStation, Canada}{\textbf{\textit{\\Certificate, User Experience Design}}}\hfill{May 2021 -- July 2021}}\\
{\makebox[7cm][l]{\bf University of Western Ontario, Canada}{\textbf{\textit{\\B.Sc. Mathematics}}}\hfill{June 2021}}\\
\end{rSection}

\begin{rSection}{Professional Experience}
\begin{rSubsection}{\makebox[7cm][l]{PinpinX, San Jose, US}\textbf{\textit{UX Designer Intern}}}{Jan. 2022 -- Present}{}{}
\item Designed responsive web and mobile experiences by translating business requirements into user flows, wireframes, interaction patterns, and production-ready visual specifications.
\item Partnered with developers, project managers, editors, and visual designers to align product hypotheses, content structure, implementation constraints, and launch priorities.
\item Used UX survey feedback to validate design assumptions and iterate on navigation, usability, and cross-platform consistency.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{Easy Group, Toronto, Canada}\textbf{\textit{Marketing Operations Associate}}}{Aug. 2021 -- Present}{}{}
\item Coordinated campaign planning, sales-support content, and operational follow-through across departments to improve execution quality and customer-facing messaging.
\item Supported sales goals by refining promotion materials, tracking campaign readiness, and translating stakeholder feedback into concrete planning updates.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{Alpha Arts, Toronto, Canada}\textbf{\textit{Co-Founder \& Designer}}}{June 2020 -- Jan. 2022}{}{}
\item Owned product discovery and UX delivery for a digital arts initiative, translating audience needs into information architecture, prototypes, launch-ready specs, and measurable design priorities.
\item Designed and implemented responsive public-facing web pages with HTML5, CSS, and JavaScript, balancing visual storytelling, accessibility, and maintainable front-end structure.
\item Coordinated content strategy, stakeholder feedback, and iteration cycles across design and development workstreams to align launches with audience engagement goals.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{GaoTek, Toronto, Canada}\textbf{\textit{Digital Marketing Assistant Intern}}}{Feb. 2021 -- June 2021}{}{}
\item Supported B2B sales enablement through CRM workflows, SEO maintenance, Google Analytics tracking, lead-oriented communication content, and campaign performance monitoring.
\item Developed web, email, and social media content for global summits and high-tech product campaigns serving audiences across 50+ countries.
\item Edited technical product writing and promotional materials for clarity, consistency, and customer fit across engineering-heavy product lines.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{PatternedScience, Montreal, Canada}\textbf{\textit{Data Analyst Intern}}}{Aug. 2020 -- Nov. 2020}{}{}
\item Built a Python-based data-analysis workflow for English-language Twitter data, combining geolocation, sentiment scoring, and COVID-related topic signals to evaluate regional emotional responses.
\item Served as main developer for an interactive static website that translated large-dataset findings into visual maps and accessible narrative summaries using Jekyll and Netlify.
\item Improved research-to-product delivery through repeatable data mining, metric design, visualization, and stakeholder-facing reporting practices.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{K11 Concepts / NWD, Hong Kong}\textbf{\textit{Digital Strategy \& Transformation Intern}}}{July 2020 -- Sept. 2020}{}{}
\item Contributed to e-commerce transformation by translating business research, competitor benchmarks, and user-centered design insights into strategic product recommendations.
\item Developed B2C information architecture, customer-experience flows, and operational workflows for 20+ provinces, aligning external buyer journeys with internal product-management needs.
\item Conducted quantitative competitor analysis across 65+ cities in Excel to support go-to-market strategy, product positioning, prioritization, and marketplace planning.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{Goldman Sachs, New York, US}\textbf{\textit{Undergrad Insight Series Participant}}}{May 2020 -- July 2020}{}{}
\item Selected from 5,000+ candidates across North America for a seven-week program with industry practitioners on strategy, sustainability, financial services, and business practice.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Research Experience}
\begin{rSubsection}{\makebox[7cm][l]{RIT CAIR / Vis-AT Research Group, US}\textbf{\textit{Graduate Research Assistant}}}{Aug. 2024 -- Present}{}{}
\item Design hypothesis-driven studies and evaluation frameworks for human-AI systems, visualization, and accessibility; selected as a National Science Foundation AWARE-AI Research Trainee (2026--2027).
\item Analyze how AI performance, risk perception, trust, and task context affect human dependence in high-stakes AI-assisted decision workflows.
\end{rSubsection}

\begin{rSubsection}{\makebox[7cm][l]{Human Factors \& Privacy Lab, Penn State, US}\textbf{\textit{Research Assistant}}}{Aug. 2022 -- May 2024}{}{}
\item Conducted HCI and human-AI experiments using interviews, survey instruments, qualitative coding, mixed-methods analysis, visualization, and peer-reviewed manuscript preparation.
\end{rSubsection}
\end{rSection}

\begin{rSection}{Selected Publications}
\begin{itemize}
\item 4 peer-reviewed publications in the ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW 2026), ACM Conference on Human Factors in Computing Systems (CHI 2026), ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW 2025), and Association for the Advancement of Artificial Intelligence (AAAI) International Conference on Web and Social Media (ICWSM 2025); topics include human-AI collaboration, trust/risk evaluation, deepfake detection, AI-synthesized face training, and visualization-supported qualitative analysis.
\end{itemize}
\end{rSection}

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Research & Experimental design, evaluation frameworks, mixed methods, qualitative coding, scoping reviews \\
Technical & Python, SQL, JavaScript, HTML/CSS, Jekyll, Netlify, Git, Linux, SEO, Google Analytics, CRM \\
Design & Figma, Sketch, InVision, Axure, Visio, Whimsical, Adobe CC, Miro, Zeplin \\
Analytics \& PM & Tableau, Excel, PowerPoint, MS Project, data visualization, metric design, campaign reporting \\
Languages & English, Mandarin \\
\end{tabular}
\end{rSection}

\end{document}
